---
title: "assignment 2"
author: "santhosh"
date: "2022-11-03"
output: html_document
---

```

### 1.	Sort flights to find the fastest flights
```{r}
arrange(flights,arr_time)
```

### 2. Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?

```{r}
dplyr::select(flights,dep_time,sched_dep_time,dep_delay)
```

### 4. Which plane (tailnum) has the worst on-time record?

```{r}
arrange(flights,desc(arr_delay),desc(dep_delay))
```

### 5. Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
select(flights,4,5,6,9)
select(flights,starts_with("dep_"),starts_with("arr_"))
select(flights,ends_with("time"),ends_with("_delay"),-c(sched_arr_time,sched_dep_time,air_time))
```

### 3. Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios: a. A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time. b. A flight is always 10 minutes late. c. A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time. d. 99% of the time a flight is on time. 1% of the time it's 2 hours late

\### a According to the scenarios arival delay is more important than dep_delay
